Computable Compressed Matrices\\Suplementary Material

### 2013-09-25 manuscript.tex
Método VLB revisado.

So far the VLB method is more wasteful than the SM, but when we add $M_{1,4} =256$  we start to save some space.

@@

 We used a total of 87 bits to store matrix $m$ with the VLB method instead of 80 bits using the SM method. However, as shall be seen later, the VLB method will be the most efficient for most matrices.

>>>>

So far the VLB method is more wasteful than the SM, but when we add $M_{1,4} 
=256$, we start to save some space.

@@

 We used a total of 87 bits to store matrix $m$ with the VLB method instead of 
80 bits using the SM method. However, as shall be seen later, the VLB method 
will be the most efficient for most matrices. \todo{adicionei} With the method 
VLB the resulting matrix is smaller than the original matrix.
